Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-07 paper.tex
fixed tables
Abstract, Intro and comments revised
All around the paper. :D

\documentclass[a4paper,10pt,twocolumn,preprint,3p]{elsarticle}

@@

An important task when publishing a new book is determining an adequate number 
of copies to be printed, but not a excesive number, as the unsold volumes will 
lead to losses.
In this paper, we face the problem of predicting total sales using cost-sensitive
ensemble methods, that can be used as decision-aid tools for publishers, which 
can provide a reliable guidance on the decision process of publishing a book. 
A real dataset including the complete sales data for books published in Spain 
across several years has been used to create forecasting models.
Results show that \emph{EXPLAIN THE RESULTS OBTAINED}.

@@

\begin{keyword}
% Antonio - to refine later
Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification  
\end{keyword}

@@

Determining the number of copies of a new book should the publisher print, the 
so called {\em print run}, for delivery to bookstores is a challenging problem.

Thus, it is extremely important to develop accurate predictive methods which 
could forecast the future sales a new book will achieve, in order to optimise 
production schedules, improve the publishing company profits and minimise 
losses \cite{Zhao2001}.

Printing an adequate number of copies, but not too many, might reduce the number 
of unsold volumes, which could lead to losses. 
In another hand, if the number of printed copies is not enough, the publisher 
company might have temporary losses due to a lack of supply.

Moreover, according to results reported in \cite{Fildes2010,Saeed2008}, reducing 
the error in estimated sales leads to the improvement of sales predictions and 
thus, in an enhancement in the whole production process.

Usually the methods used to predict book sales have
been generally based on experts' experience, who analyse data about sales and, 
taking into account their knowledge of the industry, their experience, and their 
perception about trends, could make decisions on the companies production.
However, this process might be tedious, especially when the amount of data is 
quite large. Moreover, different experts can reach different predictions from 
the same dataset \cite{Sanders1994}.

\textbf{UNDER CONSTRUCTION ;) }

@@

The rest of this paper is structured as follows: 
A detailled review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
Obtained results after extensive experimentation are presented in Section \ref{sec:experiments_results}.
Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusions_future_work}.

@@

\textbf{UNDER CONSTRUCTION ;) }

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{books_methodology}
\end{center}
\caption{Proposed methodology.}
\label{fig:methodology}
\end{figure*}
% Antonio - I like this figure, however, it seems on it that the results of the basic classifier are used as 'starting point' of the ensembles, and the results of these methods are used in the cost sensitive classification... is this correct? Otherwise, maybe we should change the design of the figure. ;D
% Hossam: I have changed the figure as Antonio suggested ;)

@@

\begin{itemize}
\item \textbf{Bagging}: 
Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced in \cite{B1996}. Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset. The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset. The final classifier's output is based on aggregating the classifiers by taking a majority or weighted vote.

\item \textbf{Boosting}: 
Boosting is an ensemble classification algorithm which was first proposed in \cite{schapire1990strength}. Boosting is based on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called Adaptive Boosting or ''Adaboost'' for short \cite{FS1997}. Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

During the learning process, Adaboost modifies the dataset by weighting its samples. These weights are updated every time a new classifier is trained to increase the focus on the difficult data instances. Consequently, the final generated classifier is a weighted combination of all trained base classifiers. According to many previous works, Adaboost is resistant to overfitting and it can outperform many other state-of-the-art classification techniques.

\item \textbf{Random Forest}:
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}

@@

The output variable which is the total sales is a categorical variable the represent the level of the quantity sold of a given book. Four categories are used to represent the total sales level: Low (L), Medium (M), High (H) and Very High (VH). Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in. Discretization of the volume of sales was conducted with the aid of experts in the domain of editorial management business by defining the the four categories.

% Antonio - We must explain how did we obtain or 'define' these categories... an expert's opinion or so. ;D
% Hossam - I have added this to the latter paragraph. Please check.

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined for each class. Precision and recall values in Table \ref{table:basic_classifiers} show that J48 classifier achieved the highest recall value of 72\% for (VH) class with 74\% precision. The second best classifier for this important class is MLP with 68\% recall and 77\% precision. Having a look at the second important class which is (H), we can see that MLP has the highest recall with 65\% and a precision of 62\%. J48 comes second for the (H) class with a slight decrease in the recall value.

\begin{table}
\caption{Classification results using basic classifiers (without print-run)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 & kNN  & NB  & J48  & MLP  & SVM\tabularnewline
\hline 
\hline 
$Accuracy$  & 0.69$\pm$0.0026 & 0.67$\pm$0.0008 & 0.7$\pm$0.004 & 0.71$\pm$0.0027 & 0.67$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{L}$  & 0.75$\pm$0.0044 & 0.86$\pm$0.0013 & 0.79$\pm$0.0071 & 0.78$\pm$0.0222 & 0.59$\pm$0.0035\tabularnewline
\hline 
$Precision_{L}$  & 0.78$\pm$0.003 & 0.73$\pm$0.0017 & 0.8$\pm$0.0049 & 0.8$\pm$0.0173 & 0.84$\pm$0.0025\tabularnewline
\hline 
\hline 
$Recall_{M}$  & 0.74$\pm$0.0034 & 0.66$\pm$0.0024 & 0.7$\pm$0.0072 & 0.71$\pm$0.0129 & 0.82$\pm$0.002\tabularnewline
\hline 
$Precision_{M}$  & 0.65$\pm$0.003 & 0.64$\pm$0.0007 & 0.68$\pm$0.0079 & 0.69$\pm$0.007 & 0.59$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{H}$  & 0.59$\pm$0.0047 & 0.53$\pm$0.0022 & 0.6$\pm$0.0099 & 0.65$\pm$0.0346 & 0.55$\pm$0.0016\tabularnewline
\hline 
$Precision_{H}$  & 0.62$\pm$0.0037 & 0.58$\pm$0.0017 & 0.62$\pm$0.0058 & 0.62$\pm$0.0109 & 0.63$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{VH}$  & 0.6$\pm$0.0073 & 0.53$\pm$0.003 & 0.72$\pm$0.0086 & 0.68$\pm$0.0336 & 0.61$\pm$0.0012\tabularnewline
\hline 
$Precision_{VH}$  & 0.79$\pm$0.0071 & 0.81$\pm$0.0032 & 0.74$\pm$0.0072 & 0.77$\pm$0.0212 & 0.78$\pm$0.0028\tabularnewline
\hline 
\end{tabular}
\label{table:basic_classifiers}
\end{table}

@@

% Antonio - Just a comment about colors of the graphs. If one prints them in grey scale it cannot be distinguished for instance H and VH lines. ;)
% Hossam- I have updated all figure as you Antonio suggested and I have added also Low and Medium results to the figures.

\begin{table}
\caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
 & RF  &  AdaBoost &  Bagging \tabularnewline
\hline 
 \hline $Accuracy$ & 0.741 $\pm$ 0.002 & 0.743 $\pm$ 0.0023 & 0.735 $\pm$ 0.0022 \tabularnewline 
 \hline 
 \hline $Recall_{L}$ & 0.796 $\pm$ 0.0038 & 0.793 $\pm$ 0.0038 & 0.792 $\pm$ 0.0048 \tabularnewline 
 \hline $Precision_{L}$ & 0.823 $\pm$ 0.0035 & 0.827 $\pm$ 0.0032 & 0.814 $\pm$ 0.0043 \tabularnewline 
 \hline 
 \hline $Recall_{M}$ & 0.748 $\pm$ 0.0033 & 0.75 $\pm$ 0.0029 & 0.738 $\pm$ 0.0038 \tabularnewline 
 \hline $Precision_{M}$ & 0.712 $\pm$ 0.0026 & 0.716 $\pm$ 0.0032 & 0.707 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{H}$ & 0.68 $\pm$ 0.0073 & 0.684 $\pm$ 0.0051 & 0.667 $\pm$ 0.0065 \tabularnewline 
 \hline $Precision_{H}$ & 0.666 $\pm$ 0.0037 & 0.667 $\pm$ 0.0029 & 0.663 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{VH}$ & 0.723 $\pm$ 0.0054 & 0.727 $\pm$ 0.0041 & 0.731 $\pm$ 0.0057 \tabularnewline 
 \hline $Precision_{VH}$ & 0.816 $\pm$ 0.0051 & 0.808 $\pm$ 0.0056 & 0.793 $\pm$ 0.0069 \tabularnewline 
\hline 
\end{tabular}
\label{table:ensemble_classifiers}
\end{table}

>>>>

\documentclass[a4paper,10pt,onecolumn,preprint,3p]{elsarticle}
% The format for draft in Elsevier is one column. ;D

@@

An important task when publishing a new book is determining an accurate number 
of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
Results show that \emph{EXPLAIN THE RESULTS OBTAINED}.

@@

\begin{keyword}
% Antonio - to refine later
Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification \sep Ensemble methods
\end{keyword}

@@

Inside the publishing process of a new book, deciding the best {\em print run}, i.e. the number of copies to be printed and delivered to bookstores, is a very challenging problem.

To this end, it is extremely important to develop accurate predictive models which could forecast the future sales a new book will achieve, in order to optimise production schedules: to improve the publishing company profits and to minimise losses \cite{Zhao2001}, due both to the excess or to the scarcity of units.
%
%Printing an adequate number of copies, but not too many, might reduce the number 
%of unsold volumes, which could lead to losses. 
%In another hand, if the number of printed copies is not enough, the publisher 
%company might have temporary losses due to a lack of supply.
%
Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.

Usually the prediction of book sales has been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge of the industry, the production process, and their perception about trends, and take decisions on the production and publication process.
However, this process might be tedious, especially when the amount of data is 
quite large. Moreover, the results are not robust, since different experts can reach different predictions from the same dataset \cite{Sanders1994}.

\textbf{UNDER CONSTRUCTION}
% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P

@@

% Antonio - We must remark that this approach is based in classification rather than regression, which is based on levels of sales (classes) instead of on numerical results. These will be easily 'explained' or justified for a (human) publisher.
% Previous work also presented the results in an intelligible way, since it offered decision trees as the last output, but they include regression computation in the leaves. Here the models/outputs will be easily interpreted.

The rest of this paper is structured as follows: 
A detailed review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
Obtained results after extensive experimentation are presented in Section \ref{sec:experiments_results}.
Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusions_future_work}.

@@

\textbf{UNDER CONSTRUCTION}
% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{books_methodology}
\end{center}
\caption{Proposed methodology.}
\label{fig:methodology}
\end{figure*}
% Antonio - I like this figure, however, it seems on it that the results of the basic classifier are used as 'starting point' of the ensembles, and the results of these methods are used in the cost sensitive classification... is this correct? Otherwise, maybe we should change the design of the figure. ;D
% Hossam: I have changed the figure as Antonio suggested ;)
% Antonio - It is better now, however, is the evaluation the last stage of the methodology? Won't we choose the best approach based on the results? Won't we compose an useful tool with it as in previous paper? I mean a decision tree or so. ;D

@@

\begin{itemize}
\item \textbf{Bagging}: 
It is also called \textit{Bootstrap aggregating} is an ensemble meta-algorithm introduced in \cite{B1996}. Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset. The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset. 
% Antonio - I cannot understand this sentence (upper one). :/
The final classifier's output is based on aggregating the base classifiers by taking a majority or weighted vote.

\item \textbf{Boosting}: 
It is an ensemble classification algorithm which was firstly proposed in \cite{schapire1990strength}. Boosting is founded on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called \textit{Adaptive Boosting} or ``AdaBoost'' for short \cite{FS1997}. AdaBoost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belonging to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

During the learning process, AdaBoost modifies the dataset by weighting its samples. These weights are updated every time a new classifier is trained to increase the focus 
% Antonio - what is the focus here?
on the difficult data instances. Consequently, the final generated classifier is a weighted combination of all trained base classifiers. According to many previous works, 
% Antonio - if you say this, you must add some references. ;P
AdaBoost is not affected 
% Antonio - 'is not affected by' -> 'avoids'?
by overfitting and it can outperform many other state-of-the-art classification techniques.

\item \textbf{Random Forest}:
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.

% Antonio - we should improve a bit this description to do it more complete. ;)

@@

The output variable which is related to the total amount of sales is a categorical variable which represent the level of the quantity sold for a given book. Thus, four categories have been considered to represent these levels: \textit{Low (L)}, \textit{Medium (M)}, \textit{High (H)}, and \textit{Very High (VH)}. Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in. The discretization of the volume of sales was conducted by an expert in the domain of editorial management business, who defined the four categories.

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}.

\begin{table*}
\caption{Classification results using basic classifiers (without print-run)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 & kNN  & NB  & J48  & MLP  & SVM\tabularnewline
\hline 
\hline 
$Accuracy$  & 0.69$\pm$0.0026 & 0.67$\pm$0.0008 & 0.7$\pm$0.004 & 0.71$\pm$0.0027 & 0.67$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{L}$  & 0.75$\pm$0.0044 & 0.86$\pm$0.0013 & 0.79$\pm$0.0071 & 0.78$\pm$0.0222 & 0.59$\pm$0.0035\tabularnewline
\hline 
$Precision_{L}$  & 0.78$\pm$0.003 & 0.73$\pm$0.0017 & 0.8$\pm$0.0049 & 0.8$\pm$0.0173 & 0.84$\pm$0.0025\tabularnewline
\hline 
\hline 
$Recall_{M}$  & 0.74$\pm$0.0034 & 0.66$\pm$0.0024 & 0.7$\pm$0.0072 & 0.71$\pm$0.0129 & 0.82$\pm$0.002\tabularnewline
\hline 
$Precision_{M}$  & 0.65$\pm$0.003 & 0.64$\pm$0.0007 & 0.68$\pm$0.0079 & 0.69$\pm$0.007 & 0.59$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{H}$  & 0.59$\pm$0.0047 & 0.53$\pm$0.0022 & 0.6$\pm$0.0099 & 0.65$\pm$0.0346 & 0.55$\pm$0.0016\tabularnewline
\hline 
$Precision_{H}$  & 0.62$\pm$0.0037 & 0.58$\pm$0.0017 & 0.62$\pm$0.0058 & 0.62$\pm$0.0109 & 0.63$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{VH}$  & 0.6$\pm$0.0073 & 0.53$\pm$0.003 & 0.72$\pm$0.0086 & 0.68$\pm$0.0336 & 0.61$\pm$0.0012\tabularnewline
\hline 
$Precision_{VH}$  & 0.79$\pm$0.0071 & 0.81$\pm$0.0032 & 0.74$\pm$0.0072 & 0.77$\pm$0.0212 & 0.78$\pm$0.0028\tabularnewline
\hline 
\end{tabular}
\label{table:basic_classifiers}
\end{table*}

It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined for each class. Precision and recall values in Table \ref{table:basic_classifiers} show that J48 classifier achieved the highest recall value of 72\% for (VH) class with 74\% precision. The second best classifier for this important class is MLP with 68\% recall and 77\% precision. Having a look at the second important class which is (H), we can see that MLP has the highest recall with 65\% and a precision of 62\%. J48 comes second for the (H) class with a slight decrease in the recall value.

@@

\begin{table*}
\caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
 & RF  &  AdaBoost &  Bagging \tabularnewline
\hline 
 \hline $Accuracy$ & 0.741 $\pm$ 0.002 & 0.743 $\pm$ 0.0023 & 0.735 $\pm$ 0.0022 \tabularnewline 
 \hline 
 \hline $Recall_{L}$ & 0.796 $\pm$ 0.0038 & 0.793 $\pm$ 0.0038 & 0.792 $\pm$ 0.0048 \tabularnewline 
 \hline $Precision_{L}$ & 0.823 $\pm$ 0.0035 & 0.827 $\pm$ 0.0032 & 0.814 $\pm$ 0.0043 \tabularnewline 
 \hline 
 \hline $Recall_{M}$ & 0.748 $\pm$ 0.0033 & 0.75 $\pm$ 0.0029 & 0.738 $\pm$ 0.0038 \tabularnewline 
 \hline $Precision_{M}$ & 0.712 $\pm$ 0.0026 & 0.716 $\pm$ 0.0032 & 0.707 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{H}$ & 0.68 $\pm$ 0.0073 & 0.684 $\pm$ 0.0051 & 0.667 $\pm$ 0.0065 \tabularnewline 
 \hline $Precision_{H}$ & 0.666 $\pm$ 0.0037 & 0.667 $\pm$ 0.0029 & 0.663 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{VH}$ & 0.723 $\pm$ 0.0054 & 0.727 $\pm$ 0.0041 & 0.731 $\pm$ 0.0057 \tabularnewline 
 \hline $Precision_{VH}$ & 0.816 $\pm$ 0.0051 & 0.808 $\pm$ 0.0056 & 0.793 $\pm$ 0.0069 \tabularnewline 
\hline 
\end{tabular}
\label{table:ensemble_classifiers}
\end{table*}
